My title

### 2024-10-23 paper/paper.qmd
Update paper model section.

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Logistic Regression Model Build up

@@

	•	pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
	•	state accounts for geographic variations in voter preferences.
	•	population_group represents different demographic categories.
	•	numeric_grade reflects the poll’s quality rating.
	•	sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
	•	methodology captures how the poll was conducted (e.g., online, phone-based, etc.).

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

```{r}
logistic_model <- readRDS(here::here(("models/logistic_model.rds")))
```

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))
plot(mlr_harris_model)
par(mfrow = c(1, 1))  # Reset plot layout

@@

# Appendix {-}
=======
# Pollster Methodology Overview and Evaluation

@@

@@

>>>>

Here we briefly describe the logistic regression model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].

## Logistic Regression Model Setup

@@

- pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
- state accounts for geographic variations in voter preferences.
- population_group represents different demographic categories.
- numeric_grade reflects the poll’s quality rating.
- sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
- methodology captures how the poll was conducted (e.g., online, phone-based, etc.).

@@

\begin{align*}
y_i | \mu_i &\sim \text{Bernoulli}(\mu_i) \\
\mu_i &= \alpha + \beta_i + \gamma_i \\
\alpha &\sim \text{Normal}(0, 2.5) \\
\beta_i &\sim \text{Normal}(0, 2.5) \\
\gamma_i &\sim \text{Normal}(0, 2.5)
\end{align*}

$logit(\mu_i) = \alpha + \beta_1 \cdot \text{pollster\_rating\_name}_i + \beta_2 \cdot \text{state}_i + \beta_3 \cdot \text{population\_group}_i + \beta_4 \cdot \text{numeric\_grade}_i + \beta_5 \cdot \text{sample\_size}_i + \beta_6 \cdot \text{methodology}_i$

```{r}
logistic_model <- readRDS(here::here(("models/logistic_model.rds")))
summary(logistic_model)
```

# Diagnostic plots for the MLR model

```{r}
par(mfrow = c(2, 2))
plot(logistic_model)
par(mfrow = c(1, 1))
```

@@

# Appendix {-}

# Pollster Methodology Overview and Evaluation

@@

# Load required library
library(caret)

# Set a seed for reproducibility
set.seed(853)
analysis_data_reduced<- analysis_data_reduced %>% na.omit(analysis_data_reduced)
# Split the data (70% training, 30% testing)
trainIndex <- createDataPartition(analysis_data_reduced$trump_win, p = 0.7, list=FALSE)
train_data <- analysis_data_reduced[trainIndex, ]
test_data <- analysis_data_reduced[-trainIndex, ]

@@

```{r}
# Make predictions on the test dataset
predicted_probabilities <- predict(logistic_model, newdata = test_data, type = "response")

# Binarize the predicted probabilities using a threshold of 0.5
predicted_classes <- ifelse(predicted_probabilities > 0.5, 1, 0)

# Confusion Matrix
conf_matrix <- confusionMatrix(factor(predicted_classes), factor(test_data$trump_win))
print(conf_matrix)

# Precision, Recall, and F1-score
precision <- posPredValue(factor(predicted_classes), factor(test_data$trump_win))
recall <- sensitivity(factor(predicted_classes), factor(test_data$trump_win))
f1_score <- 2 * ((precision * recall) / (precision + recall))

cat("Precision:", precision, "\n")
cat("Recall:", recall, "\n")
cat("F1-score:", f1_score, "\n")
```

```{r}
# Load the pre-trained logistic model from RDS
logistic_model <- readRDS(here:here("models/logistic_model.rds"))

# Calculate Trump and Harris percentages for each state (you still need to prepare the data)
analysis_data <- analysis_data %>%
  group_by(state) %>%
  mutate(
    Trump_percent = mean(case_when(candidate_name == "Donald Trump" ~ percent), na.rm = TRUE),
    Harris_percent = mean(case_when(candidate_name == "Kamala Harris" ~ percent), na.rm = TRUE)
  ) %>%
  # Create a binary outcome for prediction: 1 if Trump is predicted to win, 0 if Harris
  mutate(trump_win = ifelse(Trump_percent > Harris_percent, 1, 0))

# Create 10-fold cross-validation resampling
folds <- vfold_cv(analysis_data, v = 10)

# Fit the resamples using the loaded logistic model
cross_validation <- fit_resamples(
  logistic_model,
  data = analysis_data,
  resamples = folds,
  metrics = metric_set(accuracy, roc_auc),
  control = control_resamples(save_pred = TRUE)
)

# Collect and display metrics
collect_metrics(cross_validation) %>%
  select(.metric, mean) %>%
  knitr::kable(
    col.names = c("Metric", "Mean"),
    digits = 2,
    format.args = list(big.mark = ",")
  )

# Display confusion matrix for resampled results
conf_mat_resampled(cross_validation) %>%
  mutate(Proportion = Freq / sum(Freq)) %>%
  knitr::kable(
    digits = 2,
    format.args = list(big.mark = ","))
```
